### 2014-09-25 fundamentals/examples.tex
first cut at recycle scenario graphs and charts

>>>>

Some simple examples of recycle scenarios in Cyclus follow.  In \Cyclus,
because material is tracked as discrete objects, single-pass mox recycle is
easy to implement.  The \em{BatchReactor} archetype from \Cycamore has the
ability to accept fuel from multiple input sources with non-uniform
preference.  The dynamic resource exchange makes it easy for a reactor to
preferrentially accept recycled MOX fuel over fresh UOX fuel.  The material
flows for this simulation are shown below in figure \ref{fig:flow-modopen}.

\begin{figure}
\label{fig:flow-modopen}
\caption{Modified open 1-pass MOX recycle fuel cycle material flows.}
\begin{center}
\includegraphics{./images/flow-mod-open-1.eps}
\end{center}
\end{figure}

To switch to a fully closed fuel cycle, all that needs to be done is change
the output commodity for the \em{BatchReactor}'s spent MOX fuel.  All this
requires is a single word change in the input file resulting in the material
flows in Figure \ref{fig:flow-closed}.  Note that because the
\em{BatchReactor} always transmutes fuel into the same composition, the
nuclide level flows are not realistic for the full, multipass recycle case.

\TODO{mention how fuel fab mixes fissile and filler streams}

\begin{figure}
\label{fig:flow-closed}
\caption{Full MOX recycle (multi-pass) fuel cycle material flows.}
\begin{center}
\includegraphics{./images/flow-closed-1.eps}
\end{center}
\end{figure}

\TODO{discuss Pu buildup charts}

\begin{figure}
\label{fig:puseries-1}
\caption{bla}
\begin{center}
\includegraphics{./images/puseries-1.eps}
\end{center}
\end{figure}

\begin{figure}
\label{fig:puseries-n}
\caption{bla}
\begin{center}
\includegraphics{./images/puseries-n.eps}
\end{center}
\end{figure}
